### 2021-11-08 input/background.tex
wining space piece by piece
adapting to two columns, stilltodo. simpler problem display

\item [Dynamic partitioning and adaptive scoped broadcast:]

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \process that belonged to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).
\end{asparadesc}

>>>>

\item [Dynamic partitioning:]

In Figure~\ref{fig:partition_intuitionD}, \Process $G$ destroys its
replica. Every \process that belonged to its green partition must
choose another partition to be in. While it makes sense for
\Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).

\item [Lazy partitioning:]

\TODO{Finally, in Figure~\ref{fig:partition_intuition}, every nodes of
  the system maintains an index to every content. In systems
  comprising billions of content, this could constitute a scalability
  issue. The partitioning protocol should take advantage of boundary
  between autonomous systems in the Internet. For instance, the AS
  from France should not flood the AS from Spain unless the latter
  starts to host a replica. In addition, when the system removes its
  last source, it should stop receiving messages from other ASes
  designed to maintain the closest partition.}

\end{asparadesc}

### 2021-11-08 input/proposal.tex
adapting to two columns, stilltodo. simpler problem display

\subsection{Scoped broadcast}
\label{subsec:scoped}

@@

\begin{definition}[\label{def:lwo}Message staleness]
  A message $m$ conveys \underline{s}tale control information if the
  \process that broadcast $m$ later broadcast another message $m'$:
  $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.

@@

\input{input/figproblem.tex}

>>>>

\subsection{Scoped broadcast \TODO{Is it so important?}}
\label{subsec:scoped}

@@

\begin{definition}[\label{def:lwo}Message staleness]
  Only the latest message of a \process matters. A message $m$ conveys
  \underline{s}tale control information if the \process that broadcast
  $m$ later broadcast another message $m'$: $S(m) = \exists m': b_p(m)
  \rightarrow b_p(m')$.

@@

\input{input/figsimplerproblem.tex}
